Quality assessment measures for explainable fusion of statistical evidences of edges in PolSAR images: A First Approach

### 2023-01-26 Text/Articles/IGARSS_2023/IG23_AbstractTemplate.tex
some update in notation

The study on the applications of PolSAR data, particularly edge detection, has received increasing attention~\cite{Jin2016,Wang2018}. Edge detection in PolSAR images plays an essential role in many applications, such as speckle noise reduction, superpixel segmentation, land-cover classification, and target recognition~\cite{Xiang2016}. 
Several methods and algorithms have been proposed for edge detection in PolSAR imagery~\cite{Schou2003,Gambini2007,Nascimento2014}.

@@

Some of the most frequently used indicators of quality are the mean square error (MSE)~\cite{beaulieu2003multi}, 
the correlation (CC) coefficient~\cite{aiazzi2004spectral}, and the entropy~\cite{han2008study}:
\begin{itemize}
	\item Mean square error measures the spectral distortion introduced by the fusion process.
	$$MSE= \displaystyle \frac{\sum_{i=1}^{M}\sum_{i=1}^{N}(f(i,j)-r(i,j))^2}{M\times N}.$$
	\item The correlation coefficient measures the degree of correlation between the enhanced and the original images.
	$$CC=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2(y_i-\Bar{y})^2}}.$$
	\item The Entropy is used for measuring the richness of data in enhanced images.
	$$H=-\sum_{i=1}^{n}d(i)\log_2d(i).$$
	%%% ACF O que é d(i)?
\end{itemize}

>>>>

The study on the applications of PolSAR data, including edge detection, has received increasing attention~\cite{Jin2016,Wang2018}. Edge detection in PolSAR images plays an essential role in many applications, such as speckle noise reduction, superpixel segmentation, land-cover classification, and target recognition~\cite{Xiang2016}. 
Several methods and algorithms have been proposed for edge detection in PolSAR imagery~\cite{Schou2003,Gambini2007,Nascimento2014}.

@@

Some of the most frequently used indicators of quality are the mean square error (MSE)~\cite{beaulieu2003multi}, 
the correlation coefficient (CC)~\cite{aiazzi2004spectral}, and the entropy (H)~\cite{han2008study}:
\begin{itemize}
	\item Mean square error measures the spectral distortion introduced by the fusion process.
	$$MSE= \displaystyle \frac{\sum_{i=1}^{M}\sum_{i=1}^{N}(f(i,j)-r(i,j))^2}{M\times N}.$$
	\item The correlation coefficient measures the degree of correlation between the enhanced and the original images.
	$$CC=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2(y_i-\Bar{y})^2}}.$$
	\item The entropy is used for measuring the richness of data in enhanced images.
	$$H=-\sum_{i=1}^{n}p(i)\log_2p(i).$$
	%%% ACF O que é d(i)?
\end{itemize}
